---
title: "SeqCounter"
author: "Luca Procaccio"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SeqCounter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo = FALSE}
library(knitr)
```

```{r setup}
library(SeqCounter)
```

# Introduction

SeqCounter is a package which takes:
1) a reference genome (e.g., human hg38)
2) a set of interesting genomic regions (e.g., all 3’UTRs of coding genes)
3) a set of short search sequences (e.g., miRNA binding seeds) to be identified within the 
interesting genomics regions (exact matching)
and returns an overall count for each search sequence within the interesting genomic regions

# Example

```{r, echo=FALSE, message=FALSE}
library(TxDb.Hsapiens.UCSC.hg38.knownGene)
library(Biostrings)
```

```{r, warning=FALSE}
hg38 <- BSgenome.Hsapiens.UCSC.hg38::BSgenome.Hsapiens.UCSC.hg38
txdb <- TxDb.Hsapiens.UCSC.hg38.knownGene::TxDb.Hsapiens.UCSC.hg38.knownGene
promoters <- promoters(txdb, upstream=2000, downstream=200)
promoters <- trim(promoters)
patterns <- DNAStringSet(c("TATAAAA", "TATATAT", "TATAAAT"))
```